### 2021-06-10 paper/abstract.tex
Full version, as sent to Jörg. Manually reverted 3a,b.

\noindent

% Abstracts of Research Articles and Reports should explain to the general reader why the research was done, what was found and why the results are important.

% They should start with some brief BACKGROUND information: a sentence giving a broad introduction to the field comprehensible to the general reader, and then a sentence of more detailed background specific to your study.

Background:

Spread disease, initially NPIs, now testing and vaccines; seasonality unclear.

% This should be followed by an explanation of the OBJECTIVES/METHODS and then the RESULTS.

Objective: Provide a model that allows studying these things in conjunction, allowing for different virus strains.

Results: Along the transition to vaccination-induced herd immunity, testing is most effective, also thanks to family structures. Seasonality contributed its share.

% The final sentence should outline the main CONCLUSIONS of the study, in terms that will be comprehensible to all our readers. The Abstract is distinct from the main body of the text, and thus should not be the only source of background information critical to understanding the manuscript. Please do not include citations or abbreviations in the Abstract.

Conclusions: Frequent rapid testing should remain part of strategies to contain CoViD-19.

@@

\vspace{1cm}
\noindent JEL Classification: C63, I18

\noindent Keywords: Covid-19, agent based simulation model, public health measures

>>>>

\noindent
% Abstracts of Research Articles and Reports should explain to the general reader why
% the research was done, what was found and why the results are important. 
% 
% They should start with some brief BACKGROUND information: a sentence giving a broad
% introduction to the field comprehensible to the general reader, and then a sentence of
% more detailed background specific to your study. 
In order to slow the spread of the CoViD-19 pandemic, governments around the world have
enacted a wide set of policies limiting the transmission of the disease. Initially,
these focused on non-pharmaceutical interventions; more recently, vaccinations and
large-scale rapid testing have started to play a major role. The objective of this study
is to explain the quantitative effects of these policies on determining the course of
the pandemic, allowing for factors like seasonality or virus strains with different
transmission profiles. In order to do so, the study develops an agent-based simulation
model that is estimated on data for the second and the third wave of the CoViD-19
pandemic in Germany. The paper finds that during a period where vaccination rates rose
from 5\% to 40\%, large-scale rapid testing had the largest effect on reducing infection
numbers. 
% The final sentence should outline the main CONCLUSIONS of the study, in terms that
% will be comprehensible to all our readers. The Abstract is distinct from the main body
% of the text, and thus should not be the only source of background information critical
% to understanding the manuscript. Please do not include citations or abbreviations in
% the Abstract. 
Frequent, large-scale rapid testing should remain part of strategies to contain
CoViD-19; it can substitute for many non-pharmaceutical interventions that come at a
much larger cost to individuals, society, and the economy.

@@

\vspace{1cm}
\noindent \textbf{JEL Classification:} C63, I18

\noindent \textbf{Keywords:} CoViD-19, agent based simulation model, rapid testing,
non-pharmaceutical interventions

### 2021-06-10 paper/report.tex
Full version, as sent to Jörg. Manually reverted 3a,b.

The three dimensions of contact types are chosen so that the most common NPIs can be
modeled in great detail. NPIs affect the number of contacts or the risk of transmitting
the disease upon having physical contact. The effect of different NPIs will generally
vary across contact types. For example, a mandate to work from home will reduce the
number of work contacts to zero for a fraction of the working population. Schools and
daycare can be closed entirely, operate at reduced capacity---including an alternating
schedule---,or implement mitigation measures like masking requirements or air filters
\citep{Lessler2021}. Curfews may reduce the number of contacts in non-work/non-school
settings. In any setting, measures like masking requirements would reduce the
probability of infection associated with a contact.

@@

Despite these large effects, the results on testing likely understate the benefits. Disadvantaged groups of the population are less likely to be reached by testing campaigns; at the same time they have a higher risk to contract CoViD-19. Mandatory tests at school and at the workplace would help reach these groups, too. The same goes for ...

The tests are

 Testing: Rapid tests are cheap (less than 1\euro), just a nuisance.

Results
\begin{itemize}
    \item Advantage of testing in both cases: Recurrent. Small cost relative to other
          stuff. Certain publicness.
\end{itemize}

>>>>

The three dimensions of contact types are chosen so that the most common NPIs can be
modeled in great detail. NPIs affect the number of contacts or the risk of transmitting
the disease upon having physical contact. The effect of different NPIs will generally
vary across contact types. For example, a mandate to work from home will reduce the
number of work contacts to zero for a fraction of the working population. Schools and
daycare can be closed entirely, operate at reduced capacity---including an alternating
schedule---,or implement mitigation measures like masking requirements or air filters
\citep{Lessler2021}. Curfews may reduce the number of contacts in non-work/non-school
settings. In any setting, measures like masking requirements would reduce the
probability of infection associated with a contact
\citep{Cheng2021}\comment[id=HM]{https://science.sciencemag.org/content/early/2021/05/19/science.abg6296}

@@

Despite these large effects, the results on testing likely understate the benefits. Disadvantaged groups of the population are less likely to be reached by testing campaigns;\comment[id=HM]{seems obvious, but I did not find anything. COSMO data? We should get the raw data, btw.} at the same time they have a higher risk to contract CoViD-19.\citet{RKI-Corona-Monitoring-Bundesweit}\comment[id=HM]{\url{https://www.rki.de/DE/Content/Gesundheitsmonitoring/Studien/lid/Ergebnisse.pdf}} Mandatory tests at school and at the workplace will extend more into these groups. The same goes for individuals who exhibit a low level of compliance with CoViD-19-related regulations. Our analysis has shown that in the transition path to high levels of vaccination and possibly thereafter, large-scale rapid testing can substitute for some NPIs. This comes at a fraction of the cost. A day of the winter lockdown in Germany is estimated to have cost XXX~Euros. In early June 2021, retail prices for self-administered rapid tests are frequently less than 1~Euro.
